%-------------------------
% Resume in Latex
% Author : Damia Alyssa binti Adam Sim
% Website: www.linkedin.com/in/damia-alyssa
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{ragged2e}  % To enable \justifying


% Use Times New Roman
\usepackage{times}
\usepackage{mathptmx}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1)
                --++ (-0, 1.2)
                --++ (0.6, 0)
                --++ (0, -0.6)
                --++ (0.6, 0)
                --++ (0, -1);
            \path[draw, line width = 0.5, rounded corners=0.5]
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5)
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1)
            -- (1, 1) -- (1, 0.6);
    }
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{#2\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small#4 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/damia-alyssa}{\Large Damia Alyssa binti Adam Sim}} & \href{mailto:damialyss4@gmail.com}{damialyss4@gmail.com} \\
  \href{https://www.linkedin.com/in/damia-alyssa}{linkedin.com/in/damia-alyssa} & +6012-695-7989 \\
  \href{https://github.com/damiaalyssa}{github.com/damiaalyssa}
\end{tabular*}

%-----------Objective-----------------
\section{Objective}
\linespread{1.3}
\hspace{0.2 cm}
A passionate second-year Computer Science (Data Science) student seeking an internship from \textbf {14 July to 12 October}. I aim to gain hands-on experience by applying my skills in data analysis and programming while contributing meaningfully to both industry and society. I'm eager to learn, grow, and make a positive impact during this opportunity.

%-----------Education-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Multimedia University}{Cyberjaya, Malaysia}
    {Bachelor in Computer Science (Data Science); CGPA: 3.94/4.00, MUET: Band 4.5}{Apr. 2022 - Present}
  \resumeSubheading
    {Multimedia University}{Cyberjaya, Malaysia}
    {Foundation in Information Technology; CGPA: 3.94/4.00}{Apr. 2021 - Mar. 2022}
  \resumeSubheading
    {SMK Bandar Utama Damansara 3}{} 
    {SPM: 3A, 3B+}{2017 - 2021}
\resumeSubHeadingListEnd

%-----------Leadership experience \& involvements-----------------
\section{Leadership Experience \& Involvements}
\resumeSubHeadingListStart

  \resumeSubheading
    {Charisma Movement \href{https://www.charismamovement.com/}{\ExternalLink}}{Oct. 2024 - Present}
    {Data Analyst}{}
    \resumeItemListStart
      \resumeItem{}{Collaborated with the team to create data-driven reports and impactful visualizations that enhanced storytelling and reader engagement. Ensured data accuracy and integrity through meticulous source verification and analysis.}
    \resumeItemListEnd

  \resumeSubheading
    {Korean Language Society, MMU}{Aug. 2023 - Jan. 2025}
    {Head of Division of Culture}{}
    \resumeItemListStart
      \resumeItem{}{Led the planning and execution of cultural events to promote Korean culture, language, and arts within the university. Coordinated with team members to enhance student engagement across campus.}
    \resumeItemListEnd

  \resumeSubheading
    {IT Society MMU, Barcamp 2024 \href{https://itsocietymmu.com/barcamp-cyberjaya/}{\ExternalLink}}{May 2024 - Sept. 2024}
    {Sponsorship Committee Member}{}
    \resumeItemListStart
      \resumeItem{}{Secured sponsorships by crafting persuasive proposals and reaching out to potential sponsors.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------Projects-----------------
\section{Projects}
\resumeSubHeadingListStart
\justifying
  
  \resumeSubItem{University Aid Management \href{https://github.com/damiaalyssa/UniversityAidManagement}{\ExternalLink}}
    {: A Django-based platform streamlining financial aid applications, fund tracking, and role-based access, with real-time notifications and communication tools. It simplifies student submissions, fund disbursement, and application review for aid officers and funders.
 \textit{(Django, SQLite, Python, JavaScript)}}
  
  \resumeSubItem{K-drama Analysis \href{https://github.com/damiaalyssa/Kdrama-Analysis}{\ExternalLink}}
    {: Conducted an exploratory data analysis on a K-Drama dataset using R, focusing on genre trends, actor performance, and sentiment analysis of drama descriptions. Developed skills in data wrangling, text mining, and storytelling through visuals.
 \textit{(R, ggplot2, dplyr, tidytext)}}

   \resumeSubItem{Kwazam Chess}
    {:  A Java-based two-player chess game with unique piece mechanics, transformations, and save/load features, using OOP and UML for design and implementation.}

 
\resumeSubHeadingListEnd


%--------Programming Skills------------
\section{Skills \& Certificates}
\resumeSubHeadingListStart
  \item{\textbf{Languages}{: Malay (Native), English (Fluent), Mandarin (Fluent), Korean (Beginner)}}
  \item{\textbf{Technologies}{: HTML, CSS, Python, C++ , SQL, Java, Javascript, R}}
  \item{\textbf{Awards}{: Dean’s List – 2 semesters in Foundation, 4 semesters in Degree}}
  \item{\textbf{Certificates}{: Google Data Analytics, C++ Intermediate, Introduction to C++}}
\resumeSubHeadingListEnd

\end{document}
